### 2018-03-15 manuscript.rmd
added likelihood values for all but 1 supp. tree
added likelihood value for JTT tree
corrected
actually the correct values.
added bootstrap support

```{r supplementary trees, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Phylogenies obtained using different models of evolution. Topologies are the same. A. GTR + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories.  B. JTT + Empirically counted frequencies from alignment + FreeRate model with 6 categories. C. WAG + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. "}

@@

trees<-c(GTRtree,JTTtree,WAGtree)
trees<-lapply(trees,fix_trees)
class(trees)<-"multiPhylo"
names(trees)<-c("A. GTR20+FO+R6 ","B. JTT+F+R6","C. WAG+FO+R6")
ggtree(trees) + facet_wrap(~.id, scale="free", ncol=3) +geom_tiplab(size=2) + xlim(0, 2)

>>>>

```{r supplementary trees, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Phylogenies obtained using different models of evolution. Unlabeled nodes have support >0.99. A. GTR + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -5964623.1967; AIC score: 11929462.3933.  B. JTT + Empirically counted frequencies from alignment + FreeRate model with 6 categories. Likelihood:-5964771.2358; AIC: 11929758.4715. C. WAG + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood:-5985124.7530; AIC score: 11970465.5060 "}

@@

trees<-c(GTRtree,JTTtree,WAGtree)
trees<-lapply(trees,fix_trees)
class(trees)<-"multiPhylo"

support = as.numeric( trees[[1]]$node.label )
support[ support > 99 ] = NA
support1 = c( rep( NA, length( trees[[1]]$tip.label ) ), support )

support = as.numeric( trees[[2]]$node.label )
support[ support > 99 ] = NA
support2 = c( rep( NA, length( trees[[2]]$tip.label ) ), support )

support = as.numeric( trees[[3]]$node.label )
support[ support > 99 ] = NA
support3 = c( rep( NA, length( trees[[3]]$tip.label ) ), support )

p1<-ggtree(trees[[1]])+geom_tiplab(size=2)+geom_text(aes(label=support1),size=3, hjust=-0.1, col="red") + xlim(0, 2)+ ggtitle("A. GTR20+FO+R6")

p2<-ggtree(trees[[2]])+geom_tiplab(size=2)+geom_text(aes(label=support2),size=3, hjust=-0.1, col="red") + xlim(0, 2)+ ggtitle("B. JTT+F+R6")

p3<-ggtree(trees[[3]])+geom_tiplab(size=2)+geom_text(aes(label=support3),size=3, hjust=-0.1, col="red") + xlim(0, 2)+ ggtitle("C. WAG+FO+R6")

multiplot(p1, p2, p3, ncol=3)
